\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-22 pldi/draft.tex
Add dish cat
Add auxiliary figure

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{\detokenize{./figs/transformation-sketch.png}}
\caption{
  \textbf{Stateless parallelization transformation.}
  The \texttt{cat} node is commuted with the stateless node
  to utilize available data parallelism.
  \TODO{Correct this diagram to show the cat node before
    the node and then the cat node after the stateless
    command after the optimization. Cat node should be
    different than a circle. Maybe like an ``and'' node
    in binary circuits?}
}
\vspace{-10pt}
\label{fig:parallelization-transformation}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{\detokenize{./figs/auxiliary-transformations.png}}
\caption{
  \textbf{Auxiliary transformations.}
  \todo{Add all three of the auxiliary transformations.}
}
\vspace{-10pt}
\label{fig:auxiliary-transformations}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{\detokenize{./figs/dish_cat.pdf}}
\vspace{-28pt}
\caption{
  \textbf{Stateless parallelization transformation.}
  The \texttt{cat} node is commuted with the stateless node to utilize available data parallelism.
  \nv{Should graph be \emph{directed}?}
}
\vspace{-15pt}
\label{fig:parallelization-transformation}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{\detokenize{./figs/dish_aux.pdf}}
\caption{
  \textbf{Auxiliary transformations.}
  These augment the DFG with \ttt{cat}, \ttt{split}, and \ttt{relay} nodes.
}
\vspace{-10pt}
\label{fig:auxiliary-transformations}
\end{figure}
